---
title: 'sparklines: an htmlwidget for R'
output:
  html_document:
    theme: flatly
---

This _sparkline htmlwidget_ is based on the nifty [jQuery Sparklines](http://omnipotent.net/jquery.sparkline/#s-about).

[htmlwidgets for R](http://www.htmlwidgets.org/) has made it extremely easy to access and use html widgets from R.

### Installation

Usage is quite straightforward. First install the package using ```devtools```.

```{r, eval=FALSE}
devtools::install_github("Bart6114/sparklines")
```

### Usage

After installation you're ready to go. Let's get some data on the daily results of the GOOG stock.

```{r, warning=FALSE, message=FALSE}
library(quantmod); library(dplyr)

GOOG <-
  getSymbols("GOOG", src = 'yahoo', from = '2015-03-15', env = NULL) %>%
  as.data.frame %>%
  mutate(day_result = GOOG.Close - GOOG.Open)

GOOG_daily_result <-
  as.vector(GOOG$day_result)

GOOG_daily_result
```

Now show a nice sparkline:

```{r, warning=FALSE, message=FALSE}
library(sparklines)
sparkline(GOOG_daily_result, "line")
```

We can also configure the look and feel a bit using a named list with options such as defined at http://omnipotent.net/jquery.sparkline/#s-docs. For example:

```{r, warning=FALSE}
sparkline(GOOG_daily_result, "line", list(fillColor="white"))
```

### Chart types

Different types of charts are available in the jQuery Sparklines library. A few of them are shown below.

```{r, warning=FALSE}
sparkline(GOOG_daily_result, "line")
sparkline(GOOG_daily_result, "bar")
sparkline(GOOG_daily_result, "tristate")
sparkline(GOOG_daily_result, "box")
```


### Further information

Type ```?sparkline``` to open up the function's R documentation.

Almost all chart types and configuration options as defined at http://omnipotent.net/jquery.sparkline/#s-docs can be used.

If you encounter issues, please open an issue at this GitHub repository.
